\textbf{\Huge Problems}
%----------------------------------------------------------------------------------------
% Problem 1
%----------------------------------------------------------------------------------------
\section{Consider the following statements:}
$(1+2)^2-1^2=2^3$\\
$(1+2+3)^2-(1+2)^2=3^3$\\
$(1+2+3+4)^2-(1+2+3)^2=4^3$\\
\begin{enumerate}[(a)]
\item Based on the three statements given above, what is the next statement suggested by these?
\item What conjecture is suggested by these statements?
\item Verify the conjecture in (b).
\end{enumerate}
\textbf{\Large(a)}\\
We see that the next statement would be: $(1+2+3+4+5)^2-(1+2+3+4)^2=5^3$.\\
\textbf{\Large(b)}\\
The conjecture is $(1+2+3+4+5+...+n)^2-(1+2+3+4+...+n-1)^2=n^3$.\\
\textbf{\Large(c)}\\
Base case:\\
Let n = 2: $(1+2)^2-(1)^2 = 2^3$\\
$9-1 = 8$ so it is true.\\
We know from Theorem 6.3 that p(n) can be rewritten as
\begin{equation}
((n(n+1))/2)^2 - ((n-1(n))/2)^2 = n^3
\end{equation}
We assume p(k).
Let p(k + 1):\\
\begin{equation}
(k+1)^3 = (((k+1)(k+1+1))/2)^2 - (((k+1-1)(k+1+1-1))/2)^2 
\end{equation}
\begin{equation}
 = ((k^2+3k+2)/2)^2 - ((k^2+k)/2)^2 
\end{equation}
\begin{equation}
 = k^4/4 + 3k^3/2 + 13k^2/4 + 3k + 1 - (k^4/4 + k^3/2 + k^2/4)
\end{equation}
\begin{equation}
 = 2k^3/2 + 12k^2/4 + 3k + 1
\end{equation}
\begin{equation}
 = k^3 + 3k^2 + 3k + 1
\end{equation}
\begin{equation}
 = (k+1)^3
\end{equation}
Our conjecture was correct.{\Huge\Bat}

%----------------------------------------------------------------------------------------
% Problem 2
%----------------------------------------------------------------------------------------
\section{By an ordered partition of an integer $n\geq 2$ is meant a sequence of positive integers whose sum is n.}
For example, the ordered partitions of 3 are 3, 1 + 2, 2 + 1, 1 + 1 + 1.
\begin{enumerate}[(a)]
\item Determine the ordered partitions of 4.
\item Determine the ordered partitions of 5.
\item Make a conjecture concerning the number of ordered partitions of an integer $n\geq 2$
\end{enumerate}
\textbf{\Large(a)}\\
The ordered partitions of 4 are as following: \\
4,
 3 + 1, 1 + 3,
  2 + 2, 2 + 1 + 1, 1 + 2 + 1, 1 + 1 + 2,
   1 + 1 + 1 + 1\\
\textbf{\Large(b)}\\
The ordered partitions of 5 are as following: \\
5,
 4 + 1, 1 + 4,
  3 + 2, 3 + 1 + 1, 2 + 3, 1 + 1 + 3, 1 + 3 + 1
   2 + 2 + 1, 2 + 1 + 2, 1 + 2 + 2, 2 + 1 + 1 + 1, 1 + 2 + 1 + 1, 1 + 1 + 2 + 1, 1 + 1 + 1 + 2,
    1 + 1 + 1 + 1 + 1\\
\textbf{\Large(b)}\\
We see that 3 has 4 ordered partitions, 4 has 8 ordered partitions and 5 has 16 ordered partitions. This can also be written as 2^2, 2^3 and 2^4. This leads to the conjecture that the number of ordered partitions of an integer $n\geq 2$ is $2^{n-1}$
%----------------------------------------------------------------------------------------
% Problem 3
%----------------------------------------------------------------------------------------
\section{Express the following quantified statement in symbols:}
For every odd integer n, the integer 3n+1 is even.\\
$\forall n\in \mathbb{Z} : n = 2k+1, 3n+1 = 2k$
Part (b) \\
Prove that the statement is true.
$3(2k+1)+1 = 6k +3 +1 = 2(3k+2)$

%----------------------------------------------------------------------------------------
% Problem 4
%----------------------------------------------------------------------------------------
\section{Express the following quantified statement in symbols:}
There exists a positive integer n such that $3n+2^{n-2}$is odd.\\
$\exists n \in \mathbb{Z} : n = 2k, 3n+2^{n-2} = 2k+1$
Part (b) \\
Prove that the statement is true.
$3*2k+2^{2k-2} = 6k+4^{k-1} = 6k+4^k*1/4$\\
$6k+1^k = 6k + 1 = 2(3k) + 1$

%----------------------------------------------------------------------------------------
% Problem 5
%----------------------------------------------------------------------------------------
\section{Prove or disprove: The sum of every five consecutive integers is divisable by 5 and the sum of no six consecutive integers is divisable by 6}
$(n)+(n+1)+(n+2)+(n+3)+(n+4) = 5n+10 = 5(n+2)$\\
$(n)+(n+1)+(n+2)+(n+3)+(n+4)+(n+5) = 6n+15$\\
noget i den stil.
%----------------------------------------------------------------------------------------
% Problem 6
%----------------------------------------------------------------------------------------
\section{Consider the following statements:}
1 = 1,\\
1 + 3 = 4,\\
1 + 3 + 5 = 9,\\
1 + 3 + 5 + 7 = 16,\\
1 + 3 + 5 + 7 + 9 = 25.\\
\begin{enumerate}[(a)]
\item Based on the three statements given above, what is the next statement suggested by these?
\item What conjecture is suggested by these statements?
\item Verify the conjecture in (b) using induction.
\end{enumerate}

%----------------------------------------------------------------------------------------
% Problem 7
%----------------------------------------------------------------------------------------
\section{Using induction, prove that}
\begin{enumerate}[(a)]
\item $\forall n \in \mathbb{N}, if n\geq 2, then n^3-n is always divisable by 3$
\item $\forall n \in \mathbb{N},n < 2^n$
\end{enumerate}




