\chapter{Obtained Experiences}
During this project several experiences have been made. We will list some of them here.

\subsection{Blackfin}
The group has worked with the blackfin for the first time. Also for the first time has there been extensively preliminary research into the platform before actually working on it. This is some experience we are sure will be quite useful the next time we have to work with embedded systems. To be efficient, it is important to make good choices early in the process. Choosing the right platform early is therefore very important.

\subsection{Constraints}
During a project like this, it is important to be able to evaluate where performance and precision can be gained. The iterative process of optimizing our system consisted of one long chain of the same question: What is holding us back? To be efficient, it is important to be able to filter the big problems from the smaller ones. During tests and calculations the group has definitely gained some experiences leading to several improvements including:
Downsizing the amount of samples used in output audio. This can be downsized even more.
Removing the negative part of cross-correlation implementation
Moving the data from external to internal memory.

\subsection{From idea to product}
Not often do we get to work with a complete project in such a short timespan. The group is therefore quite satisfied having experienced the entire process from idea to working prototype. We feel we have been through a lot of different issues regarding everything from memory types to doppler and geometry - the process (but not necessarily the project) seems "complete". This experience will be valuable when working on the bachelor project.